Light and growth form interact to shape stomatal ratio among British angiosperms

### 2017-10-17 ms/ms.Rnw
updated phylo figure

Finally, phylogenetic information should improve inferences about paleoclimates because there is appreciable phylogenetic signal in stomatal ratio. The phylogenetic half-life of stomatal ratio evolution, after accounting for \el~and Raunki\ae r life form, is $\mathrm{log}(2) / \alpha = \Sexpr{round(log(2) / fitSR_lf_a$optpar, 1)}$ my (see Table~\ref{table:srAIC} for maximum likelihood estimates of $\alpha$, the return rate in the Ornstein-Uhlenbeck model of trait evolution). This lag time may indicate that evolving to the `optimum' is constrained by the shape of the fitness landscape \citep{Muir_2015} or that other unmeasured factors which affect stomatal ratio have some phylogenetic signal. Regardless of the mechanism, this fact means that researchers may be able to use data from closely related species to improve paleoenvironment reconstruction.

>>>>

Finally, phylogenetic information should improve inferences about paleoclimates because there is appreciable phylogenetic signal in stomatal ratio. The phylogenetic half-life of stomatal ratio evolution, after accounting for \el~and Raunki\ae r life form, is $\mathrm{log}(2) / \alpha = \Sexpr{round(log(2) / fitSR_lf_a$optpar, 1)}$ my (see Table~\ref{table:srAIC} for maximum likelihood estimates of $\alpha$, the return rate in the Ornstein-Uhlenbeck model of trait evolution). This lag time may indicate that evolving to the `optimum' is constrained by the shape of the fitness landscape \citep{Muir_2015} or that other unmeasured factors which affect stomatal ratio have some phylogenetic signal. Regardless of the mechanism, this fact means that researchers may be able to use data from closely related species to improve paleoenvironment reconstruction. Despite there being phylogenetic signal, residual phylogenetic variation in stomatal ratio at the broad phylogenetic scale encompassed by British angiosperms should be at stationarity. The variance in stomatal ratio, after accounting for \el~and Raunki\ae r life form, was indistinguishable at stationarity under an Ornstein-Uhlenbeck process (see Results). This may not be the case for younger clades that have radiated in the past few million years.

### 2017-10-17 ms/ms.tex
updated phylo figure

Finally, phylogenetic information should improve inferences about paleoclimates because there is appreciable phylogenetic signal in stomatal ratio. The phylogenetic half-life of stomatal ratio evolution, after accounting for \el~and Raunki\ae r life form, is $\mathrm{log}(2) / \alpha = 1.5$ my (see Table~\ref{table:srAIC} for maximum likelihood estimates of $\alpha$, the return rate in the Ornstein-Uhlenbeck model of trait evolution). This lag time may indicate that evolving to the `optimum' is constrained by the shape of the fitness landscape \citep{Muir_2015} or that other unmeasured factors which affect stomatal ratio have some phylogenetic signal. Regardless of the mechanism, this fact means that researchers may be able to use data from closely related species to improve paleoenvironment reconstruction.

>>>>

Finally, phylogenetic information should improve inferences about paleoclimates because there is appreciable phylogenetic signal in stomatal ratio. The phylogenetic half-life of stomatal ratio evolution, after accounting for \el~and Raunki\ae r life form, is $\mathrm{log}(2) / \alpha = 1.5$ my (see Table~\ref{table:srAIC} for maximum likelihood estimates of $\alpha$, the return rate in the Ornstein-Uhlenbeck model of trait evolution). This lag time may indicate that evolving to the `optimum' is constrained by the shape of the fitness landscape \citep{Muir_2015} or that other unmeasured factors which affect stomatal ratio have some phylogenetic signal. Regardless of the mechanism, this fact means that researchers may be able to use data from closely related species to improve paleoenvironment reconstruction. Despite there being phylogenetic signal, residual phylogenetic variation in stomatal ratio at the broad phylogenetic scale encompassed by British angiosperms should be at stationarity. The variance in stomatal ratio, after accounting for \el~and Raunki\ae r life form, was indistinguishable at stationarity under an Ornstein-Uhlenbeck process (see Results). This may not be the case for younger clades that have radiated in the past few million years.
